\documentclass[margin,line]{res}
\usepackage{times}
\topmargin -.1in
\oddsidemargin -.35in
\evensidemargin -.5in
\textwidth=5.45in
\textheight=10in

\begin{document}
\hfill {\sc January 2018}
\name{\huge \sc 
{Matt Taddy} \vspace*{.1in}}

\begin{resume}

\medskip
% \section{} 
% \vspace{.05in}
% \begin{tabular}{@{}p{3in}rp{2in}}
% {\bf University of Chicago Booth School of Business}  \vspace{.1cm}&\vspace{.1cm}
% \\
% {\bf Microsoft}& ~~~~~~~~~~~~~~~~~{\tt http://taddylab.com}
% \end{tabular}


% \vspace{.5cm}
% \leaders\vrule width \textwidth\vskip0.4pt

\medskip
\section{\bf PROFESSIONAL\\ POSITIONS}

{\sc Amazon}

\vspace{-.4cm}~~~~ Vice President of Economic Technology and Chief Economist for North America (since 2018)


\vspace{-.2cm}

{\sc University of Chicago Booth School of Business}

\vspace{-.4cm}~~~~ Professor of Econometrics and Statistics, 2016-2018 

\vspace{-.4cm}~~~~ Associate Professor, 2012-2016


\vspace{-.4cm} ~~~~ Assistant Professor,  2008-2012


\vspace{-.2cm}
{\sc Microsoft}

\vspace{-.4cm}~~~~ Head of Economics and Data Science for Business AI, 2017

\vspace{-.4cm}~~~~ Principal Researcher at Microsoft Research, 2016-2017


\vspace{-.2cm}
{\sc eBay}, Research Fellow, 2014-2016

\medskip
\section{\bf EDUCATION}

{\it Ph.D. Applied Mathematics and Statistics}, June 2008\\
{\sc University of California Santa Cruz}\\
Baskin School of Engineering
% Advisor: Athanasios Kottas
%`Bayesian nonparametric analysis of conditional distributions and inference for Poisson processes'

\vspace{-0.2cm}
{\it M.S. Mathematical Statistics}, June 2005\\
{\sc McGill University, Montr\'eal}\\
 Department of Mathematics and Statistics
% Advisor: Russell Steele\\
% `Variable selection for neural network treatment classification via parallel sampling'

\vspace{-0.2cm}
{\it B.A. Philosophy and Mathematics}, June 2003\\
{\sc McGill University, Montr\'eal}

\medskip
\section{\bf PUBLICATIONS}

M. Taddy (2018).  The Technological Elements of Artificial Intelligence. {\em NBER working paper 24301}.

B. Kelly, D. Papanikolaou, A. Seru, M. Taddy (2018).  Measuring Technological Innovation over the Long Run.
{\em NBER working paper 25266}.

M. Gentzkow, B. Kelly, and M. Taddy (2017).  Text as Data. {\em NBER working paper 23276}.

J. Hartford, G. Lewis, K. Leyton-Brown, M. Taddy (2017).  Counterfactual Prediction with Deep Instrumental Variables Networks.  {\it ICML 2017}.

A. Kozlowski, M. Taddy, J. Evens (2018).  The Geometry of Culture: Analyzing Meaning through Word Embeddings, with Kozlowski and Evans. {\it To appear in the American Sociological Review.}

M. Gentzkow, J. Shapiro, and M. Taddy (2018).  Measuring group differences in high dimensional choices: Method and application to Congressional speech. {\em To appear in Econometrica}.

M. Wan, D. Wang, M. Goldman, M. Taddy, J. Rao, J. Liu, D. Lymberopoulos, and J. McAuley (2017).  Modeling consumer preferences and price sensitivities from large-scale grocery shopping transaction logs. {\it Proceedings of WWW 2017.}

S. Upadhyay, K. Chang, M. Taddy, A. Kalai, and J. Zou (2017).  Beyond Bilingual: Multi-sense Word Embeddings using Multilingual
Context. Best paper winner in {\it 2nd Workshop on representation learning for NLP}.

M. Taddy (2017). One-step estimator paths for concave regularization.  {\em Journal of Computational and Graphical Statistics}.


M. Taddy (2016). Comment: A regularization scheme on word occurrence rates that improves estimation and interpretation of topical content (Airoldi and Bischof). {\it Journal of the American Statistical Association.} 

M. Taddy, M. Gardner, L. Chen, and D. Draper (2016).  Nonparametric Bayesian analysis of heterogeneous treatment effects in digital experimentation.  {\em Journal of Business and Economic Statistics}.


M. Kolar and M. Taddy (2016).  Comment: Coauthorship and citation networks for statisticians (Ji and Jin).  {\it Annals of Applied Statistics. }


M. Taddy, C. Chen, J. Yun, and M. Wyle (2015). Bayesian and empirical Bayesian forests.  Proceedings of the {\em 32nd International Conference on Machine Learning (ICML 2015)}.

M. Taddy (2015). Distributed Multinomial Regression.  {\em Annals of Applied Statistics 9}, 1395--1414.

M. Taddy (2015). Document classification by inversion of distributed language representations. Proceedings of the {\em 53rd Meeting of the Association for Computational Linguistics (ACL 2015)}.

R.G. Gramacy and M. Taddy and S. Tian.  Hockey player performance via regularized logistic regression.
To appear in the {\it Handbook of statistical methods for design and analysis in sports}, CRC press.


M. Taddy (2013).  Multinomial inverse regression for text analysis.  
{\it Journal of the American Statistical
  Association 108}, 755--770, with discussion.

M. Taddy (2013).   Rejoinder: Efficiency and structure in MNIR.  {\it Journal of the American Statistical
  Association 108}.




R.B. Gramacy and M. Taddy and S.M. Wild (2013).  Variable selection and
sensitivity analysis via dynamic trees with an application to computer
code performance tuning.  {\it Ann. of Applied
  Stat. 7}, 51--80.

M. Taddy (2013).  Measuring political sentiment on Twitter: Factor-optimal
design for multinomial inverse regression. {\it
  Technometrics 55}, 415--425.


R.B. Gramacy and S.T. Jensen and M. Taddy (2013).  Estimating player contribution in 
hockey with regularized logistic regression. {\it Journal of Quantitative Analysis of Sports 9}, 97--111.

M.  Taddy and A. Kottas (2012). Mixture modeling for marked Poisson processes.
{\it Bayesian Analysis 7}, 335--362.


M. Taddy (2012). On estimation and selection for topic models. Proceedings of the {\it 15th International Conference on
  Artificial Intelligence and Statistics (AISTATS 2012)}.


M. Taddy, R.B. Gramacy and N.G. Polson (2011). Dynamic trees for learning and design.
 {\it Journal of the American Statistical
  Association 106}, 109--123.

M. Taddy (2010). An auto-regressive mixture model for dynamic spatial
Poisson processes: Application to tracking the intensity of violent
crime.  {\it Journal of the American Statistical
  Association 105}, 1403--1417.

M.  Taddy and A. Kottas (2010). A Bayesian nonparametric approach to inference for quantile regression.
{\it Journal of Business and Economic Statistics 28}, 357--369.

C.M. Carvalho, H.F. Lopes, N.G. Polson, and M. Taddy
(2010). Particle learning for general mixtures.  {\it Bayesian
  Analysis 5}, 709--740.

H.K.H. Lee, M. Taddy, R.B. Gramacy, and G.A. Gray
(2010). Designing and analyzing a circuit device experiment using
treed Gaussian processes.  {\it Handbook of Applied
  Bayesian Analysis, Chap. 28}, Oxford University Press.

R.B. Gramacy and M. Taddy (2010). Categorical inputs, sensitivity
       analysis, optimization and importance tempering with tgp version 2, an
       R package for treed Gaussian process models. {\it Journal of Statistical Software 33}, Issue 6.


H.K.H. Lee, M. Taddy, and G.A. Gray (2010). Selection of a representative sample.
{\it Journal of Classification 27}, 41--53.

M.  Taddy, H.K.H. Lee, G.A. Gray, and J. Griffin (2009).  Bayesian guidance for robust pattern search optimization.
{\it Technometrics 51}, 389--401.

M. Taddy and A. Kottas (2009).  Markov switching Dirichlet process mixture regression.
{\it Bayesian Analysis 4}, 793--816.

M.  Taddy, B. Sans\'o and H.K.H. Lee (2009). Fast inference for statistical inverse problems.  {\it Inverse Problems 25} 085001.

R.D. Morris, A. Kottas, M. Taddy, R. Furfaro and B.D. Ganapol (2008).
A statistical framework for the sensitivity analysis of radiative transfer models.
{\it IEEE Transactions on Geoscience and Remote Sensing 46}, 4062--4074.

G.A. Gray, M. Martinez-Canales, M. Taddy, H.K.H. Lee, and R.B. Gramacy
(2006). Enhancing parallel pattern search optimization with a Gaussian
process oracle. {\it Proceedings of the 14th NECDC}.



\medskip
\section{\bf TEACHING}

{\sc Chicago Booth}

\vskip -.35cm
~{\it Big Data  2011+} {\it (`Data Mining' prior to 2014)}. 

\vskip -.45cm
~~Created the course, runs annually for 200 MBAs

\vskip -.35cm
~{\it Applied Regression Analysis 2008-2010}

\vskip -.25cm
{\sc 2013 NBER Econometrics lectures}

\vskip -.35cm
~~Two day course with
V. Chernozukov, C. Hansen, M. Gentzkow, and J. Shapiro

\vskip -.25cm
{\sc Teaching Assistant} at UCSC and McGill in mathematics, applied math, and statistics


\medskip
\section{\bf FUNDING\\AND\\AWARDS}

Microsoft Research Expedition: The ALICE Project (founder and leader), 2016-2017
\vskip -.275cm

University of Chicago, Fellow of the Computation Institute,  2014-2017 
\vskip -.275cm

Emory Williams teaching award (chosen by students), Chicago Booth, 2016.
\vskip -.275cm
McKinsey teaching award (chosen by faculty), Chicago Booth, 2016.
\vskip -.275cm

NSF Grant, Division of Social and Economic Sciences, September 2016.  

\vskip -.4cm~~~~{\it Bilateral Bargaining through the Lens of Big Data}, with  Tadelis,  Larsen, and  Backus.

\vskip -.275cm

University of Chicago Neubauer Family Faculty Fellow, 2011-2015
\vskip -.275cm

Chicago Booth Robert L. Graves Scholar,  2010 - 2011
\vskip -.275cm

Chicago Booth Fama-Miller Center Research Grant  2011-2012

\vskip -.275cm
ISBA Savage Award Honorable Mention, 2010
\vskip -.4cm
~~~~~For outstanding PhD dissertation contribution in applied Bayesian methodology
\vskip -.275cm
IBM Corporation Scholar, University of Chicago, 2009 - 2010
\vskip -.275cm
Research member of the NMFS Center for Stock Assessment Research, 2007 - 2008
\vskip -.275cm
Fonds Qu\'eb\'ecoise de la recherche sur la nature et les technologies, 2004

\vskip -.275cm
Graduate Student Researcher at
\vskip -.35cm
~~~~~{Lawrence Livermore National
  Laboratory}, 2007,  advised by Herbie Lee and Bruno Sans\'o

\vskip -.35cm
~~~~~{NASA Ames}, 2007,  advised by Athanasios Kottas and Robin
Morris

\vskip -.35cm
~~~~~{Sandia National
  Laboratories}, 2006-2007,  advised by Genetha Grey and Herbie Lee

\vskip -.35cm
~~~~~{Los Alamos National Laboratory}, 2006,  advised by Dave Higdon, Herbie
Lee, and Bruno Sans\'o.

\vskip -.35cm
~~~~~{Montr\'eal Jewish General Hospital} and
 {\sc Urgences-Sant\'e}, 2004,
RA advised by Alain Vandal.



\vskip -.275cm
Petro-Canada Olympic Torch scholarship for student athletes,  1999-2000
\vskip -.275cm
Canadian 18 {\&} under national sailing champion, men's singlehanded dinghy (laser), 1999


% \medskip
% \section{\bf SERVICE}

% Associate Editor at JASA Applications and Case Studies, 2013-2017
% \vskip -.25cm
% Associate Editor at Statistica Sinica, 2014-2017
% \vskip -.25cm
% Associate Editor at Bayesian Analysis, 2013-2017
% \vskip -.25cm
% Co-organizer of the Microsoft Digital Economics Conference, 2016.
% \vskip -.25cm
% Academic Advisory Board member for the National Opinion Research Center (NORC), 2014+
% \vskip -.25cm
% Conference Co-chair, Kilts center conference on Marketing and Big Data at Chicago Booth, 2015+
% \vskip -.25cm
% Academic Board member for Research Computing at the University of Chicago, 2014-2016
% \vskip -.25cm
% Program Chair, ASA section on Statistical Learning and Data Mining,  2014-15
% \vskip -.25cm
% Scientific Comittee member, ISBA 2014


% \medskip
% \section{\bf SOFTWARE}

% R Packages
% \vskip -.35cm

% ~~{\sf\small distrom}: {\it Distributed multinomial regression}
% \vskip -.35cm

% ~~{\sf\small gamlr}: {\it Gamma lasso concave penalty regularization paths}
% \vskip -.35cm

% ~~{\sf\small textir}: {\it Inverse regression for analysis of sentiment in text}
% \vskip -.35cm

% ~~{\sf\small maptpx}: {\it MAP estimation of latent topic models}
% \vskip -.35cm

% ~~{\sf\small dynaTree}: {\it Dynamic treed regression and classification}
% , with R.B. Gramacy
% \vskip -.35cm

% ~~{\sf\small Bmix}:
% {\it Sampling algorithms for  stick-breaking mixtures}
% \vskip -.35cm

% ~~{\sf\small tgp}:
% {\it Nonlinear regression
% with treed Gaussian processes}, with R.B. Gramacy

% \vskip -.25cm
% Contributor to the  gensim python library for natural language processing.


% \bigskip
% \section{\bf SEMINARS}

% {\bf 2017:} Norges Bank, Oslo Norway;~~California Econometrics Meeting, Stanford CA;~~University of Texas Economics Department, Austin TX;~~AEA paper session, Chicago;~~University of Florida Statistics Dept, Gainesville;~~European Commission workshop on Data Markets, Brussels;~~Columbia University Economics Dept, NYC; ABFER Econometrics Lectures, Singapore; MSR NYC Anniversary Conference panel;~~International Conference on Computational Social Science keynote, Cologne

% {\bf 2016:}
% EC2 Meeting, Toulouse;~~ WU Institute for Statistics and Mathematics, Vienna;~~ CMStatistics, Seville;~~ Harvard CS+Econ seminar;~~ MIT/Harvard Econometrics colloquium;~~ NYU Stern IOMS Department, NYC;~~ NYU Text-as-data seminar, NYC;~~ MSR Digital Economics Conference, NYC;~~ Discussion and invited lecture at the Joint Statistical Meetings (JSM), Chicago IL;~~ ISBA World Meeting, Sardinia;~~ High Dimensional Data Analysis workshop, Fields Institute, Toronto;~~ Bank of England/LBS workshop on fintech, London UK;~~ Becker center, University of Chicago;~~ MIT CSAIL, Cambridge MA;~~ Hockey analytics conference, Simon Fraser University, Vancouver


% {\bf 2015:} Columbia University Statistics Department, NYC;~~ University of Illinois at Chicago, Information and Decision Sciences;~~ Big Data workshop, Insper, S\~ao Paulo BR;~~ University of Chicago Statistics Department;~~ Duke Statistics, Durham NC;~~ Introductory overview lecture at the Joint Statistical Meetings (JSM), Seattle WA;~~ Applied Topology and Statistics workshop, University of Victoria.;~~ Association for Computational Linguistics (ACL2015), Beijing CN;~~ International Conference on Machine Learning (ICML2015), Lille FR;~~ ISBA Bayesian nonparametrics meeting, Raleigh NC;~~ Conference on economic applications of Big Data, Cambridge-INET, Cambridge UK;~~ UC Santa Cruz, Dept of Applied Math \& Stats, Santa Cruz CA;~~ Centre de recherches mathematiques workshop, Montr\'eal QC;~~ UC Berkeley Law and Economics Seminar;~~ Microsoft Research, Cambridge MA;~~ eBay research, San Jose CA;~~ UT Dallas Jindal School of Management


% {\bf 2014:} eBay research, San Jose CA;~~ Perspectives on HD data analysis, BIRS, Banff Canada;~~ ISBA Big Data discussion panel, Cancun MX;~~ University of Pennsylvania, Econ Dept, Philadelphia PA;~~ Carnegie Mellon, School of Computer Science, Pittsburgh PA;~~ Stanford, Institute for Research in Social Sciences, Stanford CA;~~ Georgetown, McCourt School of Public Policy, Washington DC;~~ `Show and Tell' seminar series, UC Research Computing Center, Chicago IL

% {\bf 2013:} International Chinese Statistics Association, Hong Kong.;~~ University of Michigan Econ + PoliSci, Ann Arbor MI;~~ Princeton Computer Science, Princeton NJ;~~ eBay Research Labs, San Jose CA;~~ NYU Stern, New York NY;~~ INFORMS Technometrics invited session, Minneapolis MN.;~~ JASA discussion session, JSM, Montr\'eal QC;~~ University of Washington Statistics, Seattle WA;~~ WCBI University of Utah, Alta UT;~~ INFORMS Computing Society Meeting, Santa Fe NM


% {\bf 2012:} SAMSI Workshop on Digital Advertising, Durham NC;~~ ISBA, Kyoto, Japan;~~ WU Vienna University of Economics and Business, Austria;~~ Department of Energy CoDA, Santa Fe NM;~~ SBIES, UC Santa Cruz, CA




% {\bf 2011:} UC Santa Cruz, Dept of Applied Math \& Stats, Santa Cruz CA;~~ Brigham Young University, Statistics Dept, Provo UT;~~ Yeditepe Conference on Bayesian Learning, Istanbul Turkey;~~ AMA Advanced Research Techniques Tutorial,  Palm Springs CA;~~ SBIES, Washington University, St Louis MO;~~ University of Toronto Department of Economics;~~ Milton Friedman Institute, University of Chicago


% {\bf 2010:} Wharton Statistics, Philadelphia PA;~~ ISBA, Alicante Spain;~~ Cambridge University Statistics Laboratory, Cambridge UK;~~ SBIES, University of Texas, Austin TX;~~ Duke University Department of Statistical Sciences, Durham NC;~~ Johannes Kepler University IFAS, Linz Austria;~~ EBEB X, Rio de Janeiro Brazil

% {\bf 2009:} INFORMS, San Diego CA;~~ BISP6, Brixen Italy;~~ Schloss Dagstuhl, Saarland Germany;~~ SAMSI Sequential MC workshop, Durham NC


% {\bf 2006-2008:} University of Chicago Graduate School of Business, Chicago IL;~~ London School of Economics, London UK;~~ RAND Corporation, Santa Monica CA;~~ Lawrence Livermore National Laboratory, Livermoretad CA;~~ ICCOPT-II, Hamilton ON;~~ BISP5, Valencia Spain;~~ SIAM-CSE, Costa Mesa CA;~~ SAMSI Computer Experiments Workshop, Vancouver BC




\end{resume}
\end{document}
